\documentclass[11pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{palatino}

\geometry{
    letterpaper,
    top=1in,
    bottom=1in,
    left=1in,
    right=1in
}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Cover Letter - Scott Weeden},
    pdfauthor={Scott Weeden}
}

% Sender information
\signature{Scott Weeden}
\address{
    Scott Weeden \\
    Killeen, Texas \\
    \href{mailto:contact@legalluminary.com}{contact@legalluminary.com} \\
    \href{https://www.legalluminary.com}{www.legalluminary.com}
}

\begin{document}

% Recipient information
\begin{letter}{
    Mr. Malcozer \\
    MBA Attorneys \\
    \href{mailto:malcozer@mbaattorneys.com}{malcozer@mbaattorneys.com} \\
    \href{https://mbaattorneys.com}{mbaattorneys.com}
}

\opening{Dear Mr. Alcozer,}

I am writing to express my strong interest in the administrative assistant position at MBA Attorneys. As a graduate student pursuing a Master's degree in Computer Science at Texas Tech University with a focused interest in applying artificial intelligence and machine learning to legal practice, I believe I offer a unique combination of technical expertise and professional capabilities that would greatly benefit your partnership.

\textbf{Technical Skills for Modern Legal Practice}

My technical background provides immediate value to your firm. I am proficient in \LaTeX{} for preparing professional legal documents with superior typesetting quality, HTML and web technologies for digital presence and client communication, and social media marketing strategies to enhance firm visibility. Most significantly, I have hands-on experience with DocuSign template creation and debugging from my work at Fisher Investments, where I handled both technical implementation and client-side data requests during the onboarding process. This expertise can streamline your document workflows and improve client experience.

At \href{https://www.legalluminary.com}{legalluminary.com}, I have demonstrated my commitment to developing AI-powered tools specifically designed for legal professionals. This platform showcases my long-term investment in bridging technology and legal practice---a vision I am eager to develop further through partnership with your firm.

\textbf{Professional Capabilities and Personal Strengths}

Beyond technical skills, I bring essential qualities that define excellence in legal support roles. I am an attentive listener who exercises sound judgment when carrying out instructions, understanding that effective legal assistance requires both precision and discretion. My friendly and personable demeanor enables me to communicate effectively with clients, making them feel heard and supported during what are often challenging times.

I have substantial experience in legal document preparation, having compiled complex legal briefs and published IEEE engineering articles---both requiring meticulous attention to detail, rigorous research, and professional presentation. I am thoroughly capable of taking detailed notes, filing court documents, and reviewing legal materials with the accuracy and care your clients deserve. Additionally, I am prepared to become a Texas-certified notary public shortly after being hired, adding another valuable capability to my service.

\textbf{Career Transition and Unique Opportunity}

While my previous positions at Fisher Investments (handling technical and client-side data requests) and ExecuSource/Home Depot Corporate (serving as an IT Security Engineer specializing in SSO integration and Identity and Access Management) were technical in nature, I am deliberately transitioning away from pure technology roles. Currently, while completing my Master's degree, I work as a substitute teacher at Shoemaker High School, which has reinforced my passion for communication, education, and service-oriented work.

I seek a position at a small or medium-sized law firm specifically because I see tremendous opportunity to enhance attorney productivity and firm profitability through thoughtful application of emerging technologies. As I pursue advanced coursework in machine learning and artificial intelligence at Texas Tech, I would be honored to customize my academic projects to develop practical tools and utilities for MBA Attorneys---creating real-world solutions that address your firm's specific needs while advancing my education.

\textbf{Commitment to Your Success}

I am not seeking to return to a technology-focused career. Instead, I am committed to learning the legal field, supporting your practice, and growing as a legal professional. My goal is to be successful in this new field by first listening, learning, and demonstrating value through reliable assistance and innovative problem-solving.

I believe MBA Attorneys represents the ideal environment for this transition: a firm where personalized client service matters, where technology can provide competitive advantage, and where a motivated assistant with both technical capabilities and genuine interpersonal skills can make a meaningful contribution.

I would welcome the opportunity to discuss how my unique background can serve your firm's needs. Thank you for considering my application. I look forward to speaking with you.

\closing{Respectfully yours,}

\end{letter}

\end{document}
